Lyman-alpha spectra from rotating outflows

### 2018-02-14 paper/paper.tex
edit

Distant galaxies are key to understand early evolutionary stages of
our Universe.
Physical conditions in those galaxies allow the emergence of a
Lyman-$\alpha$ line emission at $1216$ \AA \citep{PartridgePeebles}.
Galaxies detected through its Lyman-$\alpha$ emission receive the name of
Lyman Alpha Emitters (LAEs).

Currently LAEs are commonly targeted in wide area galaxy surveys.
The conditions that allow for the emergence of the lYa line is that
these galaxies are star forming with a low dust content. 
They have been effectively used to study galaxy evolution,
cosmology and the thermal history of the Universe.
This has been possible through the study of their spatial distribution and
the shape of their \lya emission line.

Recent improvements in instrumentation have revolutionized the kind of
studies that can be performed on LAEs.  
It is now possible to infer detailed kinematic maps for nearby galaxies.
The study of these maps would allow us to build data-driven models to
interpret the \lya spectra of unresolved galaxies, helping us to
constrain the physical conditions of the interstellar medium (ISM)
processing the \lya radiation.

>>>>

The interpretation of the Lyman-$\alpha$ emission in galaxies is
key to understand their evolutionary processes \citep{PartridgePeebles}.
Recent improvements in instrumentation have revolutionized the kind of
studies that can be performed on Lyman-$\alpha$ emitting galaxies
(LAEs.)
For instance, it is now possible to infer detailed kinematic maps for
nearby galaxies. 
The study of these maps would allow us to build data-driven models to
interpret the \lya spectra of unresolved galaxies, helping us to
constrain the physical conditions of the interstellar medium (ISM)
processing the \lya radiation.
